get_gold_set_images

### 2018-11-06 preprocessing/detector_scripts/ground_truth_creation/get_gold_set_images.Rmd
reorganize preprocessing folder, part 2

```{r}
data <- read_csv("data/final_output/mtcnn3.csv") %>%
  distinct(video, frame, .keep_all = TRUE)
```

@@

write_csv(gold_set_candidates, "data/ground_truth/gold_set_candidates2.csv")
```

>>>>

```{r}
data <- read_csv("~/Github/xs-face/data/final_output/openpose_results_truncated_2.csv") %>%
  distinct(name, frame, .keep_all = TRUE)
```

Filter images from previous ground truth (openpose only)
```{r}
old_ground_truth <- read_csv("~/Github/xs-face/data/ground_truth/gold_set_candidates2.csv")
data %<>%
  rename(video = name) %>%
  mutate(frame = sprintf("%05d", as.numeric(frame) + 1)) %>%
  anti_join(old_ground_truth) %>%
  mutate(is_face = ifelse(Nose_conf != 0, "True", "False")) %>%
  select(group, video, frame, Nose_x, Nose_y, Nose_conf, is_face)
```

@@

write_csv(gold_set_candidates, "~/Github/xs-face/data/ground_truth/gold_set_candidates_from_openpose.csv")
```
